### 2024-07-20 multiple-regression.qmd
20240720 - assumptions

@@

>>>>

## Assumptions of Multiple Regression {#sec-assumptionsRegression}

Linear regression models make the following assumptions:

- there is a linear association between the predictor variables and the outcome variable
- there is homoscedasticity of the residuals; the residuals do not differ as a function of the predictor variables or as a function of the outcome variable
- the residuals are independent; they are uncorrelated with each other
- the residuals are normally distributed

@@

## Impact of Oultiers {#sec-multipleRegressionOutliers}

[As with correlation](#sec-correlationOutliers), multiple regression can be strongly impacted by outliers.

### 2024-07-20 mythbusters.qmd
20240720 - assumptions

@@

### QB

@@

### RB

@@

### WR/TE

@@

### QB/RB/WR/TE

>>>>

For analysis, the same player contributes multiple observations of performance (i.e., multiple seasons) due to the longitudinal nature of the data.
Inclusion of multiple data points from the same player would violate the [assumption of multiple regression](#sec-assumptionsRegression) that all observations are independent.
Thus, we use mixed-effects models that allow nonindependent observations.
In our mixed-effects models, we include a random intercept for each player, to allow our model to account for players' differing level of performance.

@@

### QB {#sec-contractYearQB}

@@

### RB {#sec-contractYearRB}

@@

### WR/TE {#sec-contractYearWRTE}

@@

### QB/RB/WR/TE {#sec-contractYearQBRBWRTE}
